Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-11 prop_letter.tex
prop_letter.tex \section{Introduction} Add citations...

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers
to the fact that the results of measuring compatible sets of
observables depend on whether they are measured together or
separately.  For example, Meyer\nb\cite{PhysRevLett.83.3751} and
Mermin\nb\cite{Mermin1999} disagree on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a
mathematical statement about contextuality.  The Kochen-Specker
theorem asserts that, in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator\nb$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that one {\it can\/}
assign definite values $0$ or $1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem\nb\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration. Mermin therefore claimed that the
impact of Meyer's negative result is
``unsupportable''\nb\citep{Mermin1999}.  Discussion has continued on
whether contextuality is consistent with experimental
outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
A fundamental question is how to address this controversy by
developing mathematical theories of quantum mechanics that are
intrinsically, rather than only implicitly, consistent with the
resources available for the realistic accuracy of an actual
measurement.

>>>>

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers
to the fact that the results of measuring compatible sets of
observables depend on whether they are measured together or
separately.  For example, Meyer\nb\cite{PhysRevLett.83.3751} and
Mermin\nb\cite{Mermin1999} disagree on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a
mathematical statement about contextuality.  The Kochen-Specker
theorem asserts that, in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator\nb$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that one {\it can\/}
assign definite values $0$ or $1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem\nb\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration. Mermin therefore claimed that the
impact of Meyer's negative result is
``unsupportable''\nb\citep{Mermin1999}.  Discussion has continued on
whether contextuality is consistent with experimental
outcomes\nb\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}..
A fundamental question is how to address this controversy by
developing mathematical theories of quantum mechanics that are
intrinsically, rather than only implicitly, consistent with the
resources available for the realistic accuracy of an actual
measurement.
